\begin{frame}{Shuffle operation}
  \begin{block}{Shuffling}
    $$x\bowtie y = \{x_1 . y_1 . \dots . x_n . y_n~|~x=x_1\dots x_n\text{ and }y=y_1\dots y_n\}$$
  \end{block}

  \begin{block}{Shuffling Sets}
    Let $R_1, R_2\subseteq M$.
    $$R_1\bowtie R_2 = \{x\bowtie y~|~x\in R_1~\text{and}~y\in R_2\}$$
  \end{block}

  \begin{exampleblock}{Shuffling regular untimed languages}
    The class of regular untimed languages is closed under shuffle.\\
    What about timed languages?
  \end{exampleblock}
  
\end{frame}


\begin{frame}{Shuffling timed languages}
  \begin{alertblock}{Shuffling timed regular languages is not always regular}
  \end{alertblock}

  $R_1=\{t_1 . a . 1 . a . t_2 . a~|~t_1+t_2 = 1\}$.
  Regular language.

  \begin{figure}
    \centering
    \begin{tikzpicture}[%
        every node/.style={circle, minimum size=4pt,minimum height=4pt, inner sep=1pt, align=center},
        shorten >=2pt,
        node distance=1.6cm, >=latex
      ]
      \node [] (s0) [draw] {$x<1$};
      \node [] (s1) [draw, right=of s0] {$y\leq 1$};
      \node [] (s2) [draw, right=of s1] {$x\leq 2$};
      \node [] (s3) [draw, accepting, right=of s2] {\phantom{$x\leq 2$}};
      \path [draw] (s0) edge[->,above]  node {$y:=0$\\a} (s1)
      (s1) edge[->,above]  node {$y=1$\\a} (s2)
      (s2) edge[->,above]  node {$x=2$\\a} (s3);
    \end{tikzpicture}
  \end{figure}


  $R_2=\{1 . b . s . b ~|~ s\in\mathbb{R}\}$. Regular.

  Prove that $R_1\bowtie R_2$ is not timed regular.

  If it was, then $\{t_1.a.\mathbf{1.b.s.b}.1.a.t_2.a~|~t_1+t_2=1\}$ would be too.
\end{frame}

\begin{frame}{Shuffling timed language}
  Assume we have an automata for $\{t_1.a.\mathbf{1.b.s.b}.1.a.t_2.a~|~t_1+t_2=1\}$.
  
  After reading $t_1.a.\mathbf{1.b.s.b}.1.a$, the clocks can either be
  \begin{itemize}
  \item $t_1+s=2$
  \item $s+2$
  \item $s+1$
  \item 1
  \end{itemize}
  
  With any of these values, we can't derive a test to accept $t_2$ such that $t_1+t_2=1$.
  
  \begin{exampleblock}{Theorem}
    It is undecidable to determine whether the shuffle of two timed regular languages is timed regular.\\
    Reduction from the universality problem.
  \end{exampleblock}
\end{frame}

\begin{frame}{Corollaries}
  \begin{block}{Bounded Ressources}
    $TA(n,K)$ Timed automata with at most $n$ clocks and constants are $\leq K$.\\
    \begin{itemize}
    \item Given $\mathcal{A,B},n,K$, decide if there is $\mathcal{C} TA(n,K)$ such that $L(\mathcal{C})=L(\mathcal{A})\bowtie L(\mathcal{B})$. \textbf{Undecidable}.
    \item Given $\mathcal{A,B},n$, decide if there is $\mathcal{C}$ with at most $n$ clocks such that $L(\mathcal{C})=L(\mathcal{A})\bowtie L(\mathcal{B})$. \textbf{Undecidable}.
    \item Given $\mathcal{A,B},n,K$, decide if there is $\mathcal{C} TA$ such that $L(\mathcal{C})=L(\mathcal{A})\bowtie L(\mathcal{B})$. \textbf{Undecidable}.
    \end{itemize}
  \end{block}
  \vfill
  
    
\end{frame}

\begin{frame}{Timed B\"uchi automata}
  \begin{block}{Definition}
    Accept infinite words of $(\mathbb{R}\times\Sigma)^\omega$.
  \end{block}
  \vfill
  \begin{alertblock}{Known Result}
    The universality problem for Timed B\"uchi automata is $\Pi^1_1$-hard.
  \end{alertblock}
  \vfill
  \begin{exampleblock}{Theorems}
    Given Timed B\"uchi Automata (TBA) $\mathcal{A}$, decide if
    \begin{itemize}
    \item Its language is accepted by a deterministic TBA
    \item Its complementation is accepted by a TBA
    \end{itemize}
    Both problems are \textit{highly undecidable}. $\Pi^1_1$-hard.
  \end{exampleblock}

\end{frame}

\begin{frame}{Conclusion}
  \begin{block}{Overview}
    \begin{itemize}
    \item FORMATS'06
    \item 52 citations
    \end{itemize}
  \end{block}
  \vfill
  \begin{exampleblock}{Contribution}
    \begin{itemize}
    \item Solved several open problems
    \item Proof strategy that works for many problems
    \item Re-proved some known results
    \end{itemize}
  \end{exampleblock}
\end{frame}
